---
output: github_document
---

## `d6` package

### Generic templates for D6 research projects

This package works as a template for new research projects, under the idea of having everything (data, R scripts, functions and manuscript/reports) contained in the same package (a 'research compendium') to facilitate collaboration and promote reproducibility.


### Installation

```{r eval=FALSE}
devtools::install_github("EcoDynIZW/d6")
```


### Usage

1. First, load the package

```{r eval=FALSE}
library("d6")
```

2. Now run the function `new_project` to create a directory with all the scaffolding (slightly modified from R package structure). For example, to start a new project about tree growth, just use:

```{r eval=FALSE}
new_project("project")
```

If you want to create a private GitHub repository for the project at the same time, use instead:

```{r eval=FALSE}
new_project("project", github = TRUE, private.repo = TRUE)
```

Note that to create a GitHub repo you will need to have configured your system as explained in http://www.rdocumentation.org/packages/devtools/functions/use_github. And for Travis to run you will need to activate it at https://travis-ci.org/profile.

